Maximum Spanning Malt: Hiring World's Leading Dependency Parsers to Plant Indian Trees

### 2009-10-30 papers/2009-icon-hyderabad/paper.tex
Clanek uz se asi muze odeslat Samarovi.

% Tady je posuzování taky slepé? Až odtajním autora, nezapomenout odtajnit i acknowledgements!
\author{%Daniel Zeman\\
%Univerzita Karlova v Praze, Ústav formální a aplikované lingvistiky\\
%Malostranské náměstí 25, CZ-11800, Praha, Czechia\\ 
%\texttt{zeman@ufal.mff.cuni.cz}
}

@@

\begin{table}[ht]
\begin{centering}
%\small
\begin{tabular}{l|l|l|l|l}
& \textbf{MST} & \textbf{Malt} & \textbf{DZ} & \textbf{Vote}\\
\hline
hi & 86.16 & 82.96 & 75.12 & \XXX 86.64\\
bn & 85.70 & 80.02 & 54.38 & \XXX 78.79\\
te & 79.85 & 78.37 & 45.78 & \XXX 78.81\\
\end{tabular}
\caption{UAS on refined \textit{morph} data (POS tag, case and vibhakti concatenated). \XXX voting se pocitalo, kdyz jeste MST pracoval jen s nomorph, takze to musime prepocitat}
\label{tab:poscasevib}
\end{centering}
% Když se ke značce POS přilepí pád, ale ne vibhakti, a s tím se přetrénuje Malt parser (ostatní parsery jsme nechali beze změny, tj. MST byl natrénovaný na nomorph a DZ naopak i na vibhakti), tak Malt sám má na všech třech jazycích pořád stejné výsledky (jako v této tabulce), ale výsledky Vote se na hindštině zhorší a na zbývajících dvou jazycích zlepší: hi=85.36, bn=83.35, te=80.89.
\end{table}

@@

%\begin{compactitem}
%\item \hi{स्टैंडर्डज} \textit{(sṭaiṁḍarḍaja)} \translit{(sṭaiṁḍarḍaja)}
%\item \hi{स्टैंडर्डस} \textit{(sṭaiṁḍarḍasa)}
%\item \hi{स्टैंडर्ड्स} \textit{(sṭaiṁḍarḍsa)}
%\item \bn{সরিয়ে} Tohle je bengálsky.
%\item \te{వాడుతున్నాం} Tohle je telugsky.
%\end{compactitem}

@@

\subsection{\XXX To Do}
\begin{compactitem}
\item \XXX Parser unique errors (oracle accuracy)
\item \XXX How many times a candidate lost due to cycle prevention, and how many times this introduced an error?
\item \XXX Learning curve
\item \XXX Spočítat, kolik je ve kterém jazyce uzlů NULL.
\item \XXX znacka chunku, priklad z bengalstiny
\item \XXX casta slova, priklad z hindstiny
\item \XXX koordinace, priklad z hindstiny
\end{compactitem}

@@

We are enormously grateful to the developers of MST and Malt parsers for making their software available to the research community.

% Tohle nezapomenout odkomentovat, až budeme posílat finální verzi!
%The research has been supported by the grant 
%MSM0021620838 (Czech Ministry of Education).

>>>>

\author{Daniel Zeman\\
Univerzita Karlova v Praze, Ústav formální a aplikované lingvistiky\\
Malostranské náměstí 25, CZ-11800, Praha, Czechia\\ 
\texttt{zeman@ufal.mff.cuni.cz}
}

@@

\begin{table}[ht]
\begin{centering}
%\small
\begin{tabular}{l|l|l|l|l}
& \textbf{MST} & \textbf{Malt} & \textbf{DZ} & \textbf{Vote}\\
\hline
hi & 86.16 & 85.84 & 75.12 & \textbf{87.12}\\
bn & 85.70 & 77.31 & 54.38 & \textbf{85.82}\\
te & \textbf{79.85} & 77.78 & 45.78 & 79.70\\
\end{tabular}
\caption{UAS on refined \textit{morph} data (POS tag, case and vibhakti concatenated).}
\label{tab:poscasevib}
\end{centering}
% Když se ke značce POS přilepí pád, ale ne vibhakti, a s tím se přetrénuje Malt parser (ostatní parsery jsme nechali beze změny, tj. MST byl natrénovaný na nomorph a DZ naopak i na vibhakti), tak Malt sám má na všech třech jazycích pořád stejné výsledky (jako v této tabulce), ale výsledky Vote se na hindštině zhorší a na zbývajících dvou jazycích zlepší: hi=85.36, bn=83.35, te=80.89.
\end{table}

@@

@@

\subsection{Voting Potential}
\label{sec:votingpotential}

In order to see how much can be potentially gained from parser combination, we summarized the attachments that at least one of the parsers got correct. This \textit{oracle accuracy} gives an upper limit for the real scores we can achieve. It corresponds to the case that for every word, an oracle correctly tells which parser to ask about the word's parent. \Tref{tab:oracle} presents the oracle accuracies together with percentage of unique correct attachments that only one parser delivered. These figures give some idea of how much similar are the errors of the respective parsers to each other. Malt parser has the most unique know-how in all three languages, which could be explained by its focus on local features. Both MST and DZ can reach for global, sentence-wide relations. Note however, that the development data set is small and the percentages correspond to 42 (Malt/Bangla) or less words.

\begin{table}[ht]
\begin{centering}
%\small
\begin{tabular}{l|l|l|l|l}
& \textbf{Oracle} & \textbf{UqMST} & \textbf{UqMalt} & \textbf{UqDZ} \\
\hline
hi & 93.92 & 2.96 & \textbf{3.12} & 1.84\\
bn & 94.20 & 4.32 & \textbf{5.18} & 1.97\\
te & 88.00 & 2.37 & \textbf{5.48} & 2.07\\
\end{tabular}
\caption{Oracle accuracy for the three languages, and unique correct attachments (\%) proposed by a single parser.}
\label{tab:oracle}
\end{centering}
\end{table}

%\subsection{\XXX To Do}
%\begin{compactitem}
%\item \XXX How many times a candidate lost due to cycle prevention, and how many times this introduced an error?
%\item \XXX Learning curve
%\item \XXX Spočítat, kolik je ve kterém jazyce uzlů NULL.
%\item \XXX casta slova, priklad z hindstiny
%\item \XXX Změřit výkon kombinovaného parseru. K tomu je potřeba rozchodit skript zmeritvykon.pl, nechtěl mi fungovat.
%\end{compactitem}

@@

We are enormously grateful to the developers of MST and Malt parsers for making their software available to the research community.
The research has been supported by the grant 
MSM0021620838 (Czech Ministry of Education).
